### 2024-01-11 Paper/Paper.tex
Init

%%
%% This is file `sample-acmlarge.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmlarge')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmlarge.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{acmart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{acmart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[acmlarge]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmlicensed}
\copyrightyear{2024}
% \acmYear{2018}
% \acmDOI{XXXXXX.XXXXXXX}

%%
%% These commands are for a JOURNAL article.
% \acmJournal{POMACS}
% \acmVolume{37}
% \acmNumber{4}
% \acmArticle{111}
% \acmMonth{8}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%   	An investigation of times that a lack in good physical security practices led to a cyber security issue

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Cybersecurity: Why it gets Physical}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Isaac Boaz}
\email{isaac.k.boaz@gmail.com}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Boaz}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Cybersecurity requires many layers and aspects of security to achieved.
  This article analyzes and reviews historical occurences where a lack of
  physical security lead to a lack of cybersecurity. In addition to introduction,
  an analysis and review of such occurences will be presented.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Cybersecurity, Security, Software, Physical, Breaches}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-anonymous initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\texttt{acmsmall}}: The default journal template style.
\item {\texttt{acmlarge}}: Used by JOCCH and TAP.
\item {\texttt{acmtog}}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\texttt{sigconf}}: The default proceedings template style.
\item{\texttt{sigchi}}: Used for SIGCHI conference articles.
\item{\texttt{sigplan}}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\texttt{anonymous,review}}: Suitable for a ``double-anonymous''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \texttt{\acmSubmissionID} command to print the
  submission's unique ID on each page of the work.
\item{\texttt{authorversion}}: Produces a version of the work suitable
  for posting by the author.
\item{\texttt{screen}}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[acmlarge]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification.  As an exception, multiple authors may share one
affiliation. Authors' names should not be abbreviated; use full first
names wherever possible. Include authors' e-mail addresses whenever
possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

Note that authors' addresses are mandatory for journal articles.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for for all
articles over two pages in length, and are optional for one- and
two-page articles (or abstracts).

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

Always use midrule to separate table header rows from data rows, and
use it only for this purpose. This enables assistive technologies to
recognise table headers and support their users in navigating tables
more easily.

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  % \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader.

Figure captions are placed {\itshape below} the figure.

Every figure should also have a figure description unless it is purely
decorative. These descriptions convey what’s in the image to someone
who cannot see it. They are also used by search engine crawlers for
indexing images, and when images cannot be loaded.

A figure description must be unformatted plain text less than 2000
characters long (including spaces).  {\bfseries Figure descriptions
  should not repeat the figure caption – their purpose is to capture
  important information that is not already provided in the caption or
  the main text of the paper.} For figures that convey important and
complex new information, a short text description may not be
adequate. More complex alternative descriptions can be placed in an
appendix and referenced in a short figure description. For example,
provide a data table capturing the information in a bar chart, or a
structured list representing a graph.  For additional information
regarding how best to write figure descriptions and why doing this is
so important, please see
\url{https://www.acm.org/publications/taps/describing-figures/}.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before the command
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, a couple of articles in a proceedings (of a
  conference, symposium, workshop for example) (paginated proceedings
  article) \cite{Andler79, Hagerup1993}, a proceedings article with
  all possible elements \cite{Smith10}, an example of an enumerated
  proceedings article \cite{VanGundy07}, an informally published work
  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
  master's thesis: \cite{anisi03}, an online document / world wide web
  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
  Artifacts: \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{Multi-language papers}

Papers may be written in languages other than English or include
titles, subtitles, keywords and abstracts in different languages (as a
rule, a paper in a language other than English should include an
English title and an English abstract).  Use \verb|language=...| for
every language used in the paper.  The last language indicated is the
main language of the paper.  For example, a French paper with
additional titles and abstracts in English and German may start with
the following command
\begin{verbatim}
\documentclass[sigconf, language=english, language=german,
               language=french]{acmart}
\end{verbatim}

The title, subtitle, keywords and abstract will be typeset in the main
language of the paper.  The commands \verb|\translatedXXX|, \verb|XXX|
begin title, subtitle and keywords, can be used to set these elements
in the other languages.  The environment \verb|translatedabstract| is
used to set the translation of the abstract.  These commands and
environment have a mandatory first argument: the language of the
second argument.  See \verb|sample-sigconf-i13n.tex| file for examples
of their usage.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{description}
\item[\texttt{sidebar}:]  Place formatted text in the margin.
\item[\texttt{marginfigure}:] Place a figure in the margin.
\item[\texttt{margintable}:] Place a table in the margin.
\end{description}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-acmlarge.tex'.

### 2024-01-28 Paper/Paper.tex
More work on paper

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Cybersecurity: Why it gets Physical}
+\title{Historic Cybersecurity Breaches Caused by a Lack of Physical Security}
 
@@
 \section{Introduction}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
+In the world of software and programs, many people in the cybersecurity
+field focus on the security and practices used in their software and programs.
+However, one of the most well-known ideas for security is the idea that
+your security is only as strong as your weakest link. Just as electricity
+follows the path of least resistance, hackers and cybercriminals need only
+find a single weak point in your security to gain access to the rest of
+your system.
 
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
+Physical security is a part of cybersecurity. The act of protecting and
+securing IT assets, data, and resources from physical attacks is a part
+of cybersecurity. This article will review and analyze historical
+occurences where a lack of physical security lead to a lack or even breach
+of cybersecurity.
 
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
+\section{Basic Physical Security}
+Regardless of what a device is doing, it is always important to understand
+the physical environment and security that the device is in. Even the
+best anti-virus software cannot be protected from a malicious actor
+uninstalling it. Physical access can mean a man in the middle attack,
+power outages, or even a keylogger being installed.
 
-\section{Template Overview}
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-anonymous initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-  template parameters}.
-
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
-
-\subsection{Template Styles}
-
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
-
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
+Some basic physical security practices include:
 \begin{itemize}
-\item {\texttt{acmsmall}}: The default journal template style.
-\item {\texttt{acmlarge}}: Used by JOCCH and TAP.
-\item {\texttt{acmtog}}: Used by TOG.
+  \item Locking a device when not in use
+  \item Restricting physical access to those that need it
+  \item Locking the doors and windows of a building
+  \item Scanning and limiting who can enter a building
 \end{itemize}
 
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\texttt{sigconf}}: The default proceedings template style.
-\item{\texttt{sigchi}}: Used for SIGCHI conference articles.
-\item{\texttt{sigplan}}: Used for SIGPLAN conference articles.
-\end{itemize}
+\section{Google's Plasma Globe \texorpdfstring{\cite{Google01}}{}} 
+One of the best ways to test your security is by doing it yourself. Google
+went about this by creating a "Red Team", a team of white-hat hackers that
+were tasked with trying to hack Google. Though this task certainly includes
+doing software-based attacks, one of the successful attacks was actually
+a physical attack.
 
-\subsection{Template Parameters}
+\subsection{Attack}
+The Red Team designed a Plasma Globe that had a USB cable attached to it for power.
+Only five plasma globes were created with a malicious modification to them.
+The Red Team added an internal chip that would emulate a USB keyboard when plugged
+in to a computer. After approximately 5-10 minutes \cite{lcamtuf}, the device
+would quickly type out a command to download a larger payload from the internet.
+In order to give the device to Google's employees, the Red Team disguised the
+device as an anniversary gift from Google (based off of LinkedIn).
 
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
+While not everyone that received the device plugged it in, it only took one of
+Google's employees to plug it in for the attack be successful. The Red Team
+gained unauthorized access to the documentation on Google's Glass, which
+at the time was heavily in development.
 
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\texttt{anonymous,review}}: Suitable for a ``double-anonymous''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \texttt{\acmSubmissionID} command to print the
-  submission's unique ID on each page of the work.
-\item{\texttt{authorversion}}: Produces a version of the work suitable
-  for posting by the author.
-\item{\texttt{screen}}: Produces colored hyperlinks.
-\end{itemize}
+\subsection{Analysis}
+What ultimately allowed this attack to be successful was improper training, understanding,
+and awareness of physical security. Google's employees were not trained to be aware
+of the potential dangers of plugging in a USB device was given to them.
 
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[acmlarge]{acmart}
-\end{verbatim}
+This attack also highlights the importance of physical security. If Google employees
+were not allowed to bring in unauthorized external devices, this attack would not
+have been successful.
 
-\section{Modifications}
+\subsection{Mitigation}
+Google learned from this breach and created a software that would listen to extremely
+fast keystrokes from USB devices and block them. This software was then installed
+on all of Google's computers.
 
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
+While a software solution is a good start, it is not a complete solution. A theoretical
+slow USB device could still be used to bypass this software. A better solution would
+be to train employees to be aware of the dangers of plugging in unauthorized devices.
 
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
+\section{Now You See Me 2}
+While not a real-life example, the movie Now You See Me 2 \cite{NowYouSeeMe2} presents
+a potential example of a physical security breach. In the movie, the main characters
 
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
-
-\section{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification.  As an exception, multiple authors may share one
-affiliation. Authors' names should not be abbreviated; use full first
-names wherever possible. Include authors' e-mail addresses whenever
-possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-Note that authors' addresses are mandatory for journal articles.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-Always use midrule to separate table header rows from data rows, and
-use it only for this purpose. This enables assistive technologies to
-recognise table headers and support their users in navigating tables
-more easily.
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}[h]
-  \centering
-  % \includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{A woman and a girl in white dresses sit in an open car.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader.
-
-Figure captions are placed {\itshape below} the figure.
-
-Every figure should also have a figure description unless it is purely
-decorative. These descriptions convey what’s in the image to someone
-who cannot see it. They are also used by search engine crawlers for
-indexing images, and when images cannot be loaded.
-
-A figure description must be unformatted plain text less than 2000
-characters long (including spaces).  {\bfseries Figure descriptions
-  should not repeat the figure caption – their purpose is to capture
-  important information that is not already provided in the caption or
-  the main text of the paper.} For figures that convey important and
-complex new information, a short text description may not be
-adequate. More complex alternative descriptions can be placed in an
-appendix and referenced in a short figure description. For example,
-provide a data table capturing the information in a bar chart, or a
-structured list representing a graph.  For additional information
-regarding how best to write figure descriptions and why doing this is
-so important, please see
-\url{https://www.acm.org/publications/taps/describing-figures/}.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before the command
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, a couple of articles in a proceedings (of a
-  conference, symposium, workshop for example) (paginated proceedings
-  article) \cite{Andler79, Hagerup1993}, a proceedings article with
-  all possible elements \cite{Smith10}, an example of an enumerated
-  proceedings article \cite{VanGundy07}, an informally published work
-  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
-    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
-  master's thesis: \cite{anisi03}, an online document / world wide web
-  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
-  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
-  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
-  Artifacts: \cite{R} and \cite{UMassCitations}.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{Multi-language papers}
-
-Papers may be written in languages other than English or include
-titles, subtitles, keywords and abstracts in different languages (as a
-rule, a paper in a language other than English should include an
-English title and an English abstract).  Use \verb|language=...| for
-every language used in the paper.  The last language indicated is the
-main language of the paper.  For example, a French paper with
-additional titles and abstracts in English and German may start with
-the following command
-\begin{verbatim}
-\documentclass[sigconf, language=english, language=german,
-               language=french]{acmart}
-\end{verbatim}
-
-The title, subtitle, keywords and abstract will be typeset in the main
-language of the paper.  The commands \verb|\translatedXXX|, \verb|XXX|
-begin title, subtitle and keywords, can be used to set these elements
-in the other languages.  The environment \verb|translatedabstract| is
-used to set the translation of the abstract.  These commands and
-environment have a mandatory first argument: the language of the
-second argument.  See \verb|sample-sigconf-i13n.tex| file for examples
-of their usage.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{description}
-\item[\texttt{sidebar}:]  Place formatted text in the margin.
-\item[\texttt{marginfigure}:] Place a figure in the margin.
-\item[\texttt{margintable}:] Place a table in the margin.
-\end{description}
-
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-base}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
-
+% \bibliographystyle{ACM-Reference-Format}
+% \bibliographystyle{unsrt}
+\bibliography{bib}
 \end{document}

### 2024-01-28 Paper/Paper.tex
Add nysm and mi

@@
 \copyrightyear{2024}
-% \acmYear{2018}
-% \acmDOI{XXXXXX.XXXXXXX}
-
-%%
-%% These commands are for a JOURNAL article.
-% \acmJournal{POMACS}
-% \acmVolume{37}
-% \acmNumber{4}
-% \acmArticle{111}
-% \acmMonth{8}
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% For managing citations, it is recommended to use bibliography
-%% files in BibTeX format.
-%%
-%% You can then either use BibTeX with the ACM-Reference-Format style,
-%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
-%% support for advanced citation of software artefact from the
-%% biblatex-software package, also separately available on CTAN.
-%%
-%% Look at the sample-*-biblatex.tex files for templates showcasing
-%% the biblatex styles.
-%%
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
-
-%%
-%% end of the preamble, start of the body of the document source.
 \begin{document}
 
-%   	An investigation of times that a lack in good physical security practices led to a cyber security issue
-
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
 \title{Historic Cybersecurity Breaches Caused by a Lack of Physical Security}
 
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
 \author{Isaac Boaz}
@@
 
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
 \renewcommand{\shortauthors}{Boaz}
 
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
 \begin{abstract}
@@
 
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
 \keywords{Cybersecurity, Security, Software, Physical, Breaches}
 
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
 \maketitle
@@
 \end{itemize}
+
+Ultimately, physical security can be just as important and just as in-depth
+as cybersecurity.
 
@@
 a potential example of a physical security breach. In the movie, the main characters
+are able to breach a company's phone presentation by disguising as server maintenance,
+quickly convincing security that the original server maintainer was crazy, and 
+installing a device that would allow them to control the presentation.
 
-% \bibliographystyle{ACM-Reference-Format}
-% \bibliographystyle{unsrt}
+\subsection{Attack}
+While very entertaining, the attack in the movie is not entirely realistic. Quick uniform
+changes and pretending that you belong was presented to seem entirely plausible. Regardless,
+the important parts of the attack were that the server room was easily accessible by all staff
+without only one layer of security. The single layer was a wired door that was left open
+by the original server maintainer.
+
+Once the main character was in the server room disguised, he took a portable camera that could
+immediately print out a picture and pretended that it was "picture day" for the maintainer.
+The maintainer was not fooled by the lies, however, he was too confused and insisted that the
+character should not be there. Regardless, The main character printed out the picture and
+placed it on a badge for a mental facility.
+
+Upon calling for security, the main character was able to convince the security that the
+maintainer was crazy and that he was the real maintainer. The main character was then able
+to install a device that would allow him to control the presentation.
+
+\subsection{Analysis}
+This attack was successful because of a lack of physical security. The server room was
+easily accessible by all staff and only had a single layer of security. The maintainer
+also left the door open, allowing the main character to easily enter the room.
+With no physical keycard, identification, or other security, the main character was
+able to easily enter the room.
+
+\subsection{Mitigation}
+Ideally, the server room would have had a physical keycard, identification, or other
+security that would have prevented the main character from entering the room. The
+maintainer should have also locked the door behind him, preventing the main character
+from entering the room. Lastly, ideally the security guards would have been trained
+to be aware of social engineering and to not be easily convinced by lies.
+
+\section{Mission Impossible}
+A much more realistic example of a physical security breach is in the movie
+Mission Impossible. In the movie, Ethan Hunt (played by Tom Cruise) is tasked
+with stealing the NOC list from a CIA building. The NOC list is a list of all
+CIA agents that are currently undercover. The CIA building is heavily guarded
+and has many layers of security.
+
+\subsection{Attack}
+In the movie, we are shown the many physical layers of security that the CIA
+building has. The building has a security guard, a security camera, a keycard
+reader, and a physical key. Access to the NOC list is also restricted to only
+the physical computer that the NOC list is on. The server room employs many
+measures and monitors to prevent unauthorized access.
+
+Specifically, the server room has pressure-sensitive floors, a temperature monitor,
+sound sensor, and lasers above the ventilation system. All of these measures are disabled
+while an authorized person is in the room, and re-enabled when they leave.
+
+Ethan Hunt goes through the ventilation system, uses a mirror to reflect the
+lasers, and is slowly lowered to the floor by a wire. He then hacks into the
+computer and steals the NOC list.
+
+\subsection{Analysis}
+Here we can see that the CIA building has many layers of physical security.
+Despite all of these layers, Ethan Hunt was still able to breach the security.
+Unfortunately, the CIA building failed to account for plot armor, which is 
+a classic mistake in the field of cybersecurity.
+
+Realistically, the CIA building should have had a more secure ventilation system;
+we see that the team was able to get into the ventilation system (and the building itself)
+by disguising as firefighers. The CIA did not have proper protocols or procedures
+for fire alarms or drills, which allowed the team to easily enter the building.
+
+Additionally, requiring an authorized person to be in the room to access the
+computer would be a good requirement.
+
+\bibliographystyle{ACM-Reference-Format}
 \bibliography{bib}
@@
 \endinput
-%%
-%% End of file `sample-acmlarge.tex'.

### 2024-01-28 Paper/Paper.tex
More stuff

@@
-%%
-%% This is file `sample-acmlarge.tex',
-%% generated with the docstrip utility.
-%%
-%% The original source files were:
-%%
-%% samples.dtx  (with options: `acmlarge')
-%% 
-%% IMPORTANT NOTICE:
-%% 
-%% For the copyright see the source file.
-%% 
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-acmlarge.tex.
-%% 
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%% 
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
-%%
-%%
-%% Commands for TeXCount
-%TC:macro \cite [option:text,text]
-%TC:macro \citep [option:text,text]
-%TC:macro \citet [option:text,text]
-%TC:envir table 0 1
-%TC:envir table* 0 1
-%TC:envir tabular [ignore] word
-%TC:envir displaymath 0 word
-%TC:envir math 0 word
-%TC:envir comment 0 0
-%%
-%%
-%% The first command in your LaTeX source must be the \documentclass
-%% command.
-%%
-%% For submission and review of your manuscript please change the
-%% command to \documentclass[manuscript, screen, review]{acmart}.
-%%
-%% When submitting camera ready or to TAPS, please change the command
-%% to \documentclass[sigconf]{acmart} or whichever template is required
-%% for your publication.
-%%
-%%
-\documentclass[acmlarge]{acmart}
+\documentclass[acmsmall]{acmart}
 
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
 \AtBeginDocument{%
@@
     Bib\TeX}}}
+\setcopyright{acmlicensed}
+\copyrightyear{2024}
 
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
+\acmYear{2024}
+\acmDOI{cybersecurity.tomcruise}
+\acmJournal{TISSEC}
+\acmVolume{420}
+\acmNumber{69}
+\acmArticle{3.14}
+\acmMonth{1}
+
 \setcopyright{acmlicensed}
@@
 \author{Isaac Boaz}
+\email{boazi@wwu.edu}
 \email{isaac.k.boaz@gmail.com}
+\affiliation{%
+  \institution{Western Washington University}
+  \city{Seattle}
+  \state{Washington}
+  \country{USA}
+}
 
@@
 \keywords{Cybersecurity, Security, Software, Physical, Breaches}
+
+\begin{CCSXML}
+  <ccs2012>
+  <concept>
+  <concept_id>10003456.10003462.10003561.10003563</concept_id>
+  <concept_desc>Social and professional topics~Network access restrictions</concept_desc>
+  <concept_significance>300</concept_significance>
+  </concept>
+  <concept>
+  <concept_id>10003456.10003462.10003561.10003566</concept_id>
+  <concept_desc>Social and professional topics~Universal access</concept_desc>
+  <concept_significance>100</concept_significance>
+  </concept>
+  <concept>
+  <concept_id>10003456.10003462.10003574.10003000</concept_id>
+  <concept_desc>Social and professional topics~Social engineering attacks</concept_desc>
+  <concept_significance>500</concept_significance>
+  </concept>
+  <concept>
+  <concept_id>10003456.10003462.10003574.10003578</concept_id>
+  <concept_desc>Social and professional topics~Malware / spyware crime</concept_desc>
+  <concept_significance>100</concept_significance>
+  </concept>
+  <concept>
+  <concept_id>10002978.10002991</concept_id>
+  <concept_desc>Security and privacy~Security services</concept_desc>
+  <concept_significance>500</concept_significance>
+  </concept>
+  <concept>
+  <concept_id>10002978.10003006</concept_id>
+  <concept_desc>Security and privacy~Systems security</concept_desc>
+  <concept_significance>500</concept_significance>
+  </concept>
+  </ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Security and privacy~Security services}
+\ccsdesc[500]{Security and privacy~Systems security}
+\ccsdesc[300]{Social and professional topics~Network access restrictions}
+\ccsdesc[500]{Social and professional topics~Social engineering attacks}
+\ccsdesc[100]{Social and professional topics~Universal access}
+\ccsdesc[100]{Social and professional topics~Malware / spyware crime}
 
@@
 securing IT assets, data, and resources from physical attacks is a part
-of cybersecurity. This article will review and analyze historical
-occurences where a lack of physical security lead to a lack or even breach
-of cybersecurity.
+of cybersecurity. This article will review and analyze both fictional and
+non-fictional occurences where a lack of physical security lead to a lack
+or breach of cybersecurity.
 
@@
 best anti-virus software cannot be protected from a malicious actor
-uninstalling it. Physical access can mean a man in the middle attack,
+uninstalling it. Physical access could mean a man in the middle attack,
 power outages, or even a keylogger being installed.
@@
   \item Scanning and limiting who can enter a building
+  \item Ensuring that all devices are up to date
 \end{itemize}
@@
 While not everyone that received the device plugged it in, it only took one of
-Google's employees to plug it in for the attack be successful. The Red Team
-gained unauthorized access to the documentation on Google's Glass, which
-at the time was heavily in development.
+Google's employees to plug it in for the attack be successful. Upon successful
+execution of the script, the Red Team had access to the employee's credentials.
+Through this, they were able to send emails to other employees which had higher
+privileges. Through these emails with attachments, the Red Team was able to
+gain access to Google's Glasses internal documentation.
+
+Finally, the Red Team attempted to obtain a physical build of the Google Glasses.
+Unfortunately, due to a few typos, the Red Team caused a few red flags to be raised,
+and instead of going to pick up the build, they were met with Google's Chief Security
+Officer.
 
@@
 fast keystrokes from USB devices and block them. This software was then installed
-on all of Google's computers.
+on all of Google's computers, and publicly released \cite{Google02}.
 
@@
 
-\section{Mission Impossible}
-A much more realistic example of a physical security breach is in the movie
+\section{Mission Impossible \texorpdfstring{\cite{missionimpossible}}{}}
+A more realistic example of a physical security breach is in the movie
 Mission Impossible. In the movie, Ethan Hunt (played by Tom Cruise) is tasked
@@
 
+\subsection{Mitigation}
 Realistically, the CIA building should have had a more secure ventilation system;
@@
 
+\section{Conclusion}
+We have seen examples of physical security and how attackers may navigate around
+it. Being aware of all potential entrypoints and the human element of security is important
+to keep in mind when designing a secure system. Security exploits could stem from the
+design of a building (such as a server room being too accessible) to the training of
+its employees.
+
+Ensuring that all employees are trained to be aware of physical security and the dangers
+of social engineering is important. Additionally, ensuring that all employees are trained
+to be aware of the dangers of plugging in unauthorized devices is important. Having properly
+defined protocols and procedures for unlikely events is also important.
+Companies should internally test their security- GitLab for example similarly has a
+"Red Team" that is tasked with trying to hack GitLab \cite{GitLab}.
+
+\begin{acks}
+  I would like to thank Google for their Plasma Globe attack, and the creators of
+  Mission Impossible for their interesting portrayal of physical security.
+\end{acks}
+
 \bibliographystyle{ACM-Reference-Format}

### 2024-02-12 Paper/Paper.tex
Fix typo
More work on essay

@@
 \documentclass[acmsmall]{acmart}
+\settopmatter{printacmref=false} % Removes citation information below abstract
+\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
+\pagestyle{plain} % removes running headers
 
@@
 \acmNumber{69}
-\acmArticle{3.14}
+% \acmArticle{3.14}
 \acmMonth{1}
@@
 \copyrightyear{2024}
+
 \begin{document}
 
-\title{Historic Cybersecurity Breaches Caused by a Lack of Physical Security}
+% \title{Historic Cybersecurity Breaches Caused by a Lack of Physical Security}
+\title{An investigation of times that a lack in good physical security practices led to a cyber security issue}
 
@@
 \begin{abstract}
-  Cybersecurity requires many layers and aspects of security to achieved.
+  Cybersecurity involves many layers and aspects of security to be achieved.
   This article analyzes and reviews historical occurences where a lack of
@@
 \maketitle
+\fancyfoot{}
+\thispagestyle{empty}
 
-\section{Introduction}
+\section{Article Introduction}
 In the world of software and programs, many people in the cybersecurity
@@
 However, one of the most well-known ideas for security is the idea that
-your security is only as strong as your weakest link. Just as electricity
+a system's security is only as strong as its weakest link. Just as electricity
 follows the path of least resistance, hackers and cybercriminals need only
-find a single weak point in your security to gain access to the rest of
-your system.
+find a single weak point in a system to gain access to the rest of
+it.
 
@@
 
-\section{Basic Physical Security}
+A potential opinion of cybersecurity could fail to see (or underestimate) how
+a company's corporate culture could impact the security of the company.
+Password policies, access control, logging, and properly following
+security procedures must stem from a cybersecure-forward culture.
+
+\section{Physical Security}
 Regardless of what a device is doing, it is always important to understand
@@
 
-\section{Google's Plasma Globe \texorpdfstring{\cite{Google01}}{}}
-One of the best ways to test your security is by doing it yourself. Google
-went about this by creating a "Red Team", a team of white-hat hackers that
-were tasked with trying to hack Google. Though this task certainly includes
-doing software-based attacks, one of the successful attacks was actually
-a physical attack.
+\subsection{Cyber Secure Culture and Physical Security}
+The importance of a cyber secure culture cannot be understated. A company
+that does not have a cyber secure culture will not have employees that
+are aware of the dangers of social engineering, phishing, or plugging in
+unauthorized devices.
 
-\subsection{Attack}
+Employee training, security protocols, and procedures are all dependent
+on a culture that is aware, attentive, and proactive about security;
+which you can only get from a cyber secure culture.
+
+For instance, Google's Cyber Security Culture is stringent on including
+physical security, one example being how they handle their data centers \cite{GoogleData}.
+Google made a video describing the security of their centers. To emphasize why
+the culture of cyber-security is important,
+Stephanie Wong (a Google employee) admitted she "could talk all day
+about cloud security, (but)physical security (at Google) is still pretty new to me" \cite{GoogleDataVideo}.
+
+Google's Data Centers are a good example of how physical security is an important
+aspect of cybersecurity.
+
+\section{Google's Plasma Globe}
+One of the best ways to test security is by testing, verifying, and self-auditing
+how well the security system holds up. Google went about this by creating a
+"Red Team" \cite{GoogleRedTeamBlog}, a team of white-hat hackers that were tasked with trying to hack Google.
+Though this task certainly includes doing software-based attacks, one of the successful
+attacks was a physical attack.
+
+\subsection{Google's Plan of Attack}
 The Red Team designed a Plasma Globe that had a USB cable attached to it for power.
@@
 The Red Team added an internal chip that would emulate a USB keyboard when plugged
-in to a computer. After approximately 5-10 minutes \cite{lcamtuf}, the device
-would quickly type out a command to download a larger payload from the internet.
+in to a computer. After approximately 5-10 minutes, the device would
+quickly type out a command to download a larger payload from the internet \cite{GoogleGlobeBlog}.
 In order to give the device to Google's employees, the Red Team disguised the
@@
 privileges. Through these emails with attachments, the Red Team was able to
-gain access to Google's Glasses internal documentation.
+gain access to Google's Glasses internal documentation \cite{GoogleGlobeVideo}.
 
@@
 and instead of going to pick up the build, they were met with Google's Chief Security
-Officer.
+Officer \cite{GoogleGlobeVideo}.
 
-\subsection{Analysis}
-What ultimately allowed this attack to be successful was improper training, understanding,
-and awareness of physical security. Google's employees were not trained to be aware
-of the potential dangers of plugging in a USB device was given to them.
+\subsection{Attack Analysis}
+Ultimately, this attack was a phishing attack. The Red Team was able to convince
+Google's employees to plug in a USB device that was given to them. The Red Team
+was able to gain access to Google's Glasses internal documentation by using the
+employee's credentials.
+
+Google's physical security culture did not account for the dangers of plugging in
+unauthorized devices. While Google's employees may have been aware of the dangers
+of USB devices, mistakes can happen or people can forget about security.
+Re-inforcing the importance of a cyber secure culture and the dangers of social
+engineering is important.
 
@@
 the important parts of the attack were that the server room was easily accessible by all staff
-without only one layer of security. The single layer was a wired door that was left open
+with only one layer of security. The single layer was a wired door that was left open
 by the original server maintainer.
@@
 \subsection{Attack}
-In the movie, we are shown the many physical layers of security that the CIA
+The move shows the many physical layers of security that the CIA
 building has. The building has a security guard, a security camera, a keycard
@@
 \section{Conclusion}
-We have seen examples of physical security and how attackers may navigate around
-it. Being aware of all potential entrypoints and the human element of security is important
+Being aware of all potential entrypoints and the human element of security is important
 to keep in mind when designing a secure system. Security exploits could stem from the

### 2024-02-12 Paper/Paper.tex
Update paper

@@
 Stephanie Wong (a Google employee) admitted she "could talk all day
-about cloud security, (but)physical security (at Google) is still pretty new to me" \cite{GoogleDataVideo}.
+about cloud security, (but) physical security (at Google) is still pretty new to me" \cite{GoogleDataVideo}.
 
@@
 how well the security system holds up. Google went about this by creating a
-"Red Team" \cite{GoogleRedTeamBlog}, a team of white-hat hackers that were tasked with trying to hack Google.
-Though this task certainly includes doing software-based attacks, one of the successful
-attacks was a physical attack.
+"Red Team" \cite{GoogleRedTeamBlog}, a team of white-hat hackers that were tasked with
+trying to hack Google (a testament to their cyber-security culture).
+Though this job includes software-based attacks,
+one of the successful attacks was a physical attack.
 
@@
 In order to give the device to Google's employees, the Red Team disguised the
-device as an anniversary gift from Google (based off of LinkedIn).
+device as an anniversary gift from Google (using LinkedIn to find anniversaries) \cite{GoogleGlobeVideo}.
 
@@
 was able to gain access to Google's Glasses internal documentation by using the
-employee's credentials.
+employee's credentials \cite{GoogleGlobeVideo}.
 
@@
 
-\subsection{Mitigation}
+\subsection{Mitigation and Response}
 Google learned from this breach and created a software that would listen to extremely
 fast keystrokes from USB devices and block them. This software was then installed
-on all of Google's computers, and publicly released \cite{Google02}.
+on Google's computers, and the software was publicly released \cite{GoogleUSB,GoogleRedTeamBlog}.
 
-While a software solution is a good start, it is not a complete solution. A theoretical
-slow USB device could still be used to bypass this software. A better solution would
-be to train employees to be aware of the dangers of plugging in unauthorized devices.
+While a software solution is a good start, it is not a complete solution. A theoretically
+slow USB device could still be used to bypass this software. Cybersecurity hinges
+on a solid cyber secure culture, and humans are the core of that culture.
+
+Whether a USB device is found in the parking lot or given as a gift, it is important
+to ensure that employees are aware of the dangers of plugging in unauthorized devices.
+Thankfully, the source of the attack was not a malicious actor, a testament to 
+Google's cyber secure culture.
+
+\section{Remote Hacking of Oldsmar's Water Treatment System}
+An interesting idea of physical security is the idea of remote physical security.
+The Oldsmar water treatment plant in Florida was hacked in February 2021. The
+attacker was able to remotely access the system
+"through a dormant software called TeamViewer" \cite{CCNFlorida}.
+Unfortunately, not much is known about the attack, and Martina Dier (a spokeswoman
+for TeamViewer) stated "Based on cooperative information sharing, a diligent technical
+investigation did not find any indication for suspicious connection activity via our
+platform" \cite{CCNFlorida}.
+
+\section{Method of Attack}
+It is believed that the attacker was able to remotely access the system through
+TeamViewer. The attacker was able to increase the amount of sodium hydroxide (lye)
+in the water from 100 parts per million to 11,100 parts per million.
 

### 2024-02-13 Paper/Paper.tex
More work

@@
 \documentclass[acmsmall]{acmart}
+\usepackage{fancyhdr}
+
 \settopmatter{printacmref=false} % Removes citation information below abstract
 \renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
-\pagestyle{plain} % removes running headers
 
@@
 \acmNumber{69}
-% \acmArticle{3.14}
 \acmMonth{1}
@@
 \begin{document}
-
-% \title{Historic Cybersecurity Breaches Caused by a Lack of Physical Security}
 \title{An investigation of times that a lack in good physical security practices led to a cyber security issue}
@@
 \maketitle
+
 \fancyfoot{}
@@
 
-Ultimately, physical security can be just as important and just as in-depth
-as cybersecurity.
+Ultimately, physical security is necessary to ensure proper cybersecurity.
 
@@
 
-\section{Method of Attack}
-It is believed that the attacker was able to remotely access the system through
-TeamViewer. The attacker was able to increase the amount of sodium hydroxide (lye)
-in the water from 100 parts per million to 11,100 parts per million.
+\subsection{Method of Attack}
+It is believed that the attacker was able to remotely access the system (supposedly)
+through TeamViewer. The attacker was able to increase the amount of sodium hydroxide (lye)
+in the water from 100 parts per million to 11,100 parts per million. Thankfully,
+the system's operator noticed the change and reverted it back to the normal levels.
 
-\section{Now You See Me 2}
-While not a real-life example, the movie Now You See Me 2 \cite{NowYouSeeMe2} presents
-a potential example of a physical security breach. In the movie, the main characters
-are able to breach a company's phone presentation by disguising as server maintenance,
-quickly convincing security that the original server maintainer was crazy, and
-installing a device that would allow them to control the presentation.
+\cite{CCNFlorida} ultimately concludes that the attack was done remotely. The
+water treatment system was outdated and not kept up-to-date to proper security
+standards. "Gualtieri said the water treatment facility currently uses a Google
+Chrome product for remote access. The Oldsmar water treatment system is also using
+the Windows 7 operating system, which was released in 2009" \cite{CCNFlorida}.
 
-\subsection{Attack}
-While very entertaining, the attack in the movie is not entirely realistic. Quick uniform
-changes and pretending that you belong was presented to seem entirely plausible. Regardless,
-the important parts of the attack were that the server room was easily accessible by all staff
-with only one layer of security. The single layer was a wired door that was left open
-by the original server maintainer.
+\subsection{Attack Analysis}
+The allowance of remote access to Oldsmar's water treatment system was a major
+security concern. A lack of proper security standards and outdated software
+contributed to the attack being successful \cite{CCNFlorida}. A cyber secure-forward
+culture would have ensured that any remote access was authenticated, validated,
+logged, and audited.
 
-Once the main character was in the server room disguised, he took a portable camera that could
-immediately print out a picture and pretended that it was "picture day" for the maintainer.
-The maintainer was not fooled by the lies, however, he was too confused and insisted that the
-character should not be there. Regardless, The main character printed out the picture and
-placed it on a badge for a mental facility.
+Physical elements of a cyber secure culture could include requiring a physical
+security key, VPN, or timed access to the system. The Hill \cite{HillArticle}
+admits that "Unfortunately, that water treatment facility is the rule rather than
+the exception. When an organization is struggling to make payroll and to keep systems
+on a generation of technology created in the last decade, even the basics in cybersecurity
+often are out of reach."
 
-Upon calling for security, the main character was able to convince the security that the
-maintainer was crazy and that he was the real maintainer. The main character was then able
-to install a device that would allow him to control the presentation.
+Ultimately a cyber secure culture needs to take into account maintenance and
+upkeep of the physical systems.
 
-\subsection{Analysis}
-This attack was successful because of a lack of physical security. The server room was
-easily accessible by all staff and only had a single layer of security. The maintainer
-also left the door open, allowing the main character to easily enter the room.
-With no physical keycard, identification, or other security, the main character was
-able to easily enter the room.
+\subsection{Mitigation and Response}
+A follow-up article by CyberScoop \cite{CyberScoop} reveals that it may not have
+been a cyber-attack at all, and that it could have been an unintentional action by an
+employee.
 
-\subsection{Mitigation}
-Ideally, the server room would have had a physical keycard, identification, or other
-security that would have prevented the main character from entering the room. The
-maintainer should have also locked the door behind him, preventing the main character
-from entering the room. Lastly, ideally the security guards would have been trained
-to be aware of social engineering and to not be easily convinced by lies.
+"The FBI concluded there was nothing, no evidence of any access from the outside,
+and that it was likely the same employee that was purported to be a hero for catching
+it, was actually banging on his keyboard" \cite{CyberScoop}.
 
-\section{Mission Impossible \texorpdfstring{\cite{missionimpossible}}{}}
-A more realistic example of a physical security breach is in the movie
-Mission Impossible. In the movie, Ethan Hunt (played by Tom Cruise) is tasked
-with stealing the NOC list from a CIA building. The NOC list is a list of all
-CIA agents that are currently undercover. The CIA building is heavily guarded
-and has many layers of security.
+Even though this may not have been an actual outsider attack, the potential was certainly
+still present. According to \cite{CyberScoop}, "a data leak containing the email
+addresses and passwords with two domains belonging to Oldsmar surfaced days before the
+breach occurred".
 
-\subsection{Attack}
-The move shows the many physical layers of security that the CIA
-building has. The building has a security guard, a security camera, a keycard
-reader, and a physical key. Access to the NOC list is also restricted to only
-the physical computer that the NOC list is on. The server room employs many
-measures and monitors to prevent unauthorized access.
+With a lack of proper financial resoruces, it is difficult to ensure that the
+water treatment system is up-to-date and secure.
 
-Specifically, the server room has pressure-sensitive floors, a temperature monitor,
-sound sensor, and lasers above the ventilation system. All of these measures are disabled
-while an authorized person is in the room, and re-enabled when they leave.
+Another interesting perspective of cyber security culture is how it relates to
+federal and public policy. The Biden Administration is slowly making progress
+to have cyber-security requirements, and the Environmental Protection Agency released
+a mandate for public water systems to "evaluate the adequacy" of any digital defenses
+through sanitation surveys \cite{CyberScoopEPA}.
 
-Ethan Hunt goes through the ventilation system, uses a mirror to reflect the
-lasers, and is slowly lowered to the floor by a wire. He then hacks into the
-computer and steals the NOC list.
+\section{Credit Card Skimmers}
+An interesting example of a physical security breach is the use of credit card skimmers.
+Credit card skimmers are devices that are placed on top of a credit card reader that
+are able to read and store the information of a credit card. The skimmer is then
+retrieved by the attacker and the information is used to make unauthorized purchases \cite{FBISkimming}.
 
-\subsection{Analysis}
-Here we can see that the CIA building has many layers of physical security.
-Despite all of these layers, Ethan Hunt was still able to breach the security.
-Unfortunately, the CIA building failed to account for plot armor, which is
-a classic mistake in the field of cybersecurity.
+While not be a direct physical security breach, the use of credit card skimmers
+is directly related to cyber security, as credit card information can be viewed
+as a form of digital information.
 
-\subsection{Mitigation}
-Realistically, the CIA building should have had a more secure ventilation system;
-we see that the team was able to get into the ventilation system (and the building itself)
-by disguising as firefighers. The CIA did not have proper protocols or procedures
-for fire alarms or drills, which allowed the team to easily enter the building.
+Though the mindset and knowledge of card skimming may not wholly be a part of a
+cyber secure culture, being aware of the current dangers and threats is important
+to a cyber secure culture. Customers, credit card companies, and businesses all
+need to be aware of the dangers of credit card skimmers.
 
-Additionally, requiring an authorized person to be in the room to access the
-computer would be a good requirement.
+In one instance, six people were arrested and charged with using credit card skimmers
+to steal over \$5 million dollars from credit unions and banks \cite{FBISkimming}.
+This provides a critical reminder for the importance of physical security when it comes
+to cybersecurity. No matter how secure the software of an ATM is, a credit card skimmer
+can still be placed on top of it.
+
+\subsection{The Culture of Credit Card Skimming}
+While the typical scope of a security culture may be based off of a company's
+policies, executives, and employees, cultures are not limited to just companies.
+The cyber-secure culture of a city, state, or country can also be evaluated,
+analyzed, and improved. The Federal Bureau of Investigation (FBI) has a page
+dedicated to credit card skimming, and the FBI is working to educate the public
+about the dangers of credit card skimming \cite{FBISkimming}.
 
@@
 defined protocols and procedures for unlikely events is also important.
-Companies should internally test their security- GitLab for example similarly has a
+Companies should internally test their security- GitLab for example (similar to Google) has a
 "Red Team" that is tasked with trying to hack GitLab \cite{GitLab}.
 
-\begin{acks}
-  I would like to thank Google for their Plasma Globe attack, and the creators of
-  Mission Impossible for their interesting portrayal of physical security.
-\end{acks}
-
-\bibliographystyle{ACM-Reference-Format}
+\bibliographystyle{unsrtnat}
 \bibliography{bib}

### 2024-02-26 Paper/1/Paper.tex
Start work on paper

--- 2024-02-13 Paper/Paper.tex
@@
     Bib\TeX}}}
-\setcopyright{acmlicensed}
-\copyrightyear{2024}
-
-\acmYear{2024}
-\acmDOI{cybersecurity.tomcruise}
-\acmJournal{TISSEC}
-\acmVolume{420}
-\acmNumber{69}
-\acmMonth{1}
-
-\setcopyright{acmlicensed}
-\copyrightyear{2024}
 
@@
 through TeamViewer. The attacker was able to increase the amount of sodium hydroxide (lye)
-in the water from 100 parts per million to 11,100 parts per million. Thankfully,
+in the water from 100 parts per million to 11,100 parts per million. Luckily,
 the system's operator noticed the change and reverted it back to the normal levels.
@@
 
+Lastly, a culture is not limited to just a company. A city, state, or country can also
+have a culture of security. Informing family, friends, and the public about the dangers
+of social engineering, phishing, and plugging in unauthorized devices is important.
+
 \bibliographystyle{unsrtnat}

### 2024-02-26 Paper/2/Paper.tex
Start work on paper

\documentclass[acmsmall]{acmart}
\usepackage{fancyhdr} 
\usepackage{listings}

\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

\begin{document}
\title{The design flaw of npm and how `everything' broke it}

\author{Isaac Boaz}
\email{boazi@wwu.edu}
\email{isaac.k.boaz@gmail.com}
\affiliation{%
  \institution{Western Washington University}
  \city{Seattle}
  \state{Washington}
  \country{USA}
}

\renewcommand{\shortauthors}{Boaz}

\begin{abstract}
  npm (Node Package Manager) is a popular package manager owned by Microsoft that allows developers
  to share node packages and libraries. This article will review and analyze the design flaw of npm
  and how it was broken by a single package. This article will also review how Microsoft responded to
  the incident and what actions they took to prevent it from happening again.
\end{abstract}

\keywords{npm, design flaws, everything, left-pad}

\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10003456.10003462.10003561.10003563</concept_id>
  <concept_desc>Social and professional topics~Network access restrictions</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10003456.10003462.10003561.10003566</concept_id>
  <concept_desc>Social and professional topics~Universal access</concept_desc>
  <concept_significance>100</concept_significance>
  </concept>
  <concept>
  <concept_id>10003456.10003462.10003574.10003000</concept_id>
  <concept_desc>Social and professional topics~Social engineering attacks</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10003456.10003462.10003574.10003578</concept_id>
  <concept_desc>Social and professional topics~Malware / spyware crime</concept_desc>
  <concept_significance>100</concept_significance>
  </concept>
  <concept>
  <concept_id>10002978.10002991</concept_id>
  <concept_desc>Security and privacy~Security services</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10002978.10003006</concept_id>
  <concept_desc>Security and privacy~Systems security</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Security services}
\ccsdesc[500]{Security and privacy~Systems security}
\ccsdesc[300]{Social and professional topics~Network access restrictions}
\ccsdesc[500]{Social and professional topics~Social engineering attacks}
\ccsdesc[100]{Social and professional topics~Universal access}
\ccsdesc[100]{Social and professional topics~Malware / spyware crime}

\maketitle

\fancyfoot{}
\thispagestyle{empty}

\section{Article Introduction}
Design flaws in software can sometimes lead to security breaches. More often than
not, it is these types of breaches that are the most popularized. However, sometimes
a design flaw can lead to a catastrophic failure that was not even intended
(or initiated) by a bad actor.
With over 1.3 million packages as of April 14th, 2021 \cite{npmblog-stats}, npm is
the world's largest software registry \cite{aboutnpm,w3schools}. As a
result, it has been heavily relied upon by developers for years.

Needless to say, the npm registry is a critical piece of infrastructure for the
entire JavaScript community (and by extension 99\% of websites \cite{w3techs}). Developers
expected that the npm registry would be reliable, secure, and complete. However, the
left-pad incident in 2016 \cite{npmblog-leftpad} and the everything package incident
in 2023 \cite{youtube-everything} have shown that the npm registry is not as reliable
as developers had hoped.

\section{Historical Background}
\subsection{Introduction}
One of the most infamous events in the history of npm was the left-pad incident.
Azer Koçulu is a software developer who was working on a personal project called
kik \cite{qz}. Coincidentally, Kik was also the name of a company in
Ontario, Canada \cite{qz, crunchbase}. The company reached out to Koçulu
requesting that he change the name of his project. Koçulu refused, and the company
proceeded to file a complaint with npm \cite{qz}. npm then decided to transfer the name
kik to the company, which caused Koçulu to remove all of his packages from the
npm registry, stating

"I want all my modules to be deleted including my account, along with this package.
I don't wanna be a part of NPM anymore. If you don't do it, let me know how do it quickly.
I think I have the right of deleting all my stuff from NPM." \cite{medium-mikeroberts}

\subsection{The left-pad package}
As a result of Koçulu's deciscion, all of his packages (including left-pad) were removed
from the npm registry. Despite being only 17 lines of code \cite{github-leftpad-code},
millions of packages relied on left-pad \cite{github-leftpad-dependency}. As a result,
many packages that directly or indirectly relied on left-pad broke, including React,
Babel, and Atom.

After an attempt to publish left-pad under a new version failed (due to some major
dependencies relying on the old version specificially, which was no longer available),
npm resulted to restoring the package from a backup \cite{npmblog-leftpad}. The total
downtime taken to restore the backup was 2.5 hours \cite{npmblog-leftpad}.

With the first ever unprecedented un-unpublishing of a package, npm was able to restore
the left-pad package and the packages that relied on it.

\subsection{Mitigation and Prevention}
Once the left-pad incident was resolved, npm published a blog post detailing the
incident and the steps they planned to take to prevent it from happening again \cite{npmblog-leftpad}.

`We will make it harder to un-publish a version of a package if doing so would break other packages.
We are still fleshing out the technical details of how this will work. Like any registry change,
we will of course take our time to consider and implement it with care.' \cite{npmblog-leftpad}

npm ended up enacting two policies relating to unpublishing packages. The first policy applied on
packages that were less than 72 hours old, allowing unpublishing as long as `no other packages
in the npm Public Registry depend on your package' \cite{npm-docs-unpublishing}.

The second policy applied to packages that were older than 72 hours, allowing unpublishing as long
as three conditions were met \cite{npm-docs-unpublishing}:
\begin{enumerate}
  \item no other packages in the npm Public Registry depend on it
  \item it had less than 300 downloads over the last week
  \item it has a single owner/maintainer
\end{enumerate}

With these new policies in place, npm hoped to prevent a similar incident from happening again.
However, these new policies lead towards a new design flaw.

\section{The everything package}
\subsection{Everything's Creation}
In 2023, a developer by the name PatrickJS decided to work on a package called `everything'.
He teamed up with Evan Boehs, another developer to work on creating an npm package that
would declare every single package in the npm registry as a dependency. This invovled
working around some obscure npm limitations, such as the maximum number of dependencies
being around 800 \cite{youtube-everything}, and the maxiumum package size being 10 MB \cite{youtube-everything}.

In order to work around these limitations, PatrickJS and Evan Boehs decided to chunk their
dependencies into smaller packages \lstinline|@everything-registry/chunk-0| through to \\
\lstinline|@everything-registry/chunk-4|. At the time there was approximately 2.5 million
packages in the npm registry \cite{youtube-everything}, so sub-chunking was also required.

Unsurprisingly, npm also has a rate limit on how quickly packages can be published. Thus,
PatrickJS and Evan Boehs used a GitHub Action workflow to publish the packages \cite{youtube-everything}.

\subsection{The Aftermath}
Upon publishing of the `everything' package in Dec 2023 \cite{npm-everything},
PatrickJS and Evan Boehs had (unintentionally) disabled unpublishing every package ever on
the npm registry \cite{youtube-everything}. This was an unforseen consequence of the new
unpublishing policies that npm had put in place after the left-pad incident. Namely,
\textit{every package was now a dependency of the `everything' package},
and thus, could not be unpublushed, regardless of age. \lstinline|everything| itself could
not be removed, as it had one dependency: \lstinline|everything-else| \cite{npm-everything-else}.

This was also caused by the fact that the `everything' package depended on a `*' version
of all of its packages, which meant that it matched any version of each of its packages.

\subsection{Historic Related Incidents}
npm was not a strange to packages and projects before `everything'.

\subsubsection{no-one-left-behind}
was an npm package that was created in 2018 that similarly depended
on 1,000 npm packages \cite{npm-no-one-left-behind-dependencies}. npm managed to remove
the package before it caused significant damage \cite{npm-no-one-left-behind-security}.
It was then re-uploaded under a different name, this time with 33,000 dependencies \cite{socket-everything}.

\subsubsection{hoarders}
was a package that was created near the early conception of npm (2012) that also depended
on 11,000 packages at its inception \cite{github-hoarders-dependencies}. Isaac Schluter (
the founder of npm) talked with the creator of the package and convinced him to unpublish it
\cite{github-hoarders}.  A few years later in Aug 19, 2021

\bibliographystyle{unsrtnat}
\bibliography{bib}

\appendix
\section{Reading Resources}
Azer Koçulu himself wrote a blog post about the incident, which can be found at \cite{medium-azer}.

\end{document}
\endinput

### 2024-02-26 Paper/2/Paper.tex
More work, 4 pages is so long

@@
 Upon publishing of the `everything' package in Dec 2023 \cite{npm-everything},
-PatrickJS and Evan Boehs had (unintentionally) disabled unpublishing every package ever on
-the npm registry \cite{youtube-everything}. This was an unforseen consequence of the new
-unpublishing policies that npm had put in place after the left-pad incident. Namely,
-\textit{every package was now a dependency of the `everything' package},
-and thus, could not be unpublushed, regardless of age. \lstinline|everything| itself could
-not be removed, as it had one dependency: \lstinline|everything-else| \cite{npm-everything-else}.
+PatrickJS and Evan Boehs had (unintentionally) disabled unpublishing every
+package ever on the npm registry \cite{youtube-everything}. This was an
+unforseen consequence of the new unpublishing policies that npm had put in place
+after the left-pad incident. Namely, \textit{every package was now a dependency
+  of the `everything' package}, and thus, could not be unpublushed, regardless of
+age. \lstinline|everything| itself could not be removed, as it had one
+dependency: \lstinline|everything-else| \cite{npm-everything-else}.
 
@@
 \subsection{Historic Related Incidents}
-npm was not a strange to packages and projects before `everything'.
+npm was not a stranger to packages and projects before `everything'.
 
@@
 \subsubsection{hoarders}
-was a package that was created near the early conception of npm (2012) that also depended
-on 11,000 packages at its inception \cite{github-hoarders-dependencies}. Isaac Schluter (
-the founder of npm) talked with the creator of the package and convinced him to unpublish it
-\cite{github-hoarders}.  A few years later in Aug 19, 2021
+was a package created by Josh Holbrook that was created near the conception of npm (2012) that
+also depended on 11,000 packages at its inception \cite{github-hoarders-dependencies}.
+Isaac Schluter (the founder of npm) talked with the creator of the package and convinced
+him to unpublish it \cite{github-hoarders}.  A few years later in Aug 19, 2021, Josh Holbrook
+found a way to work around having a heavy load on npm.
+
+`now, rather than installing the utilities as direct dependencies, hoarders
+installs them lazily, on-the-fly. this change is practically seamless - simply
+reach for the utility like you would normally and hoarders will do the rest! the
+only requirements are npm and an internet connection.' \cite{github-hoarders}
+
+\subsection{Response}
+PatrickJS and Evan Boehs weren't aware of the consequences of their actions
+until they realized that they had broken the npm registry
+\cite{youtube-everything}. They reached out to npm and created an issue on the
+GitHub repository documenting and explaining the issue
+\cite{bleepingcomputer-everything}.
+
+\section{Microsoft's Response}
 

### 2024-02-26 Paper/2/Paper.tex
More work on paper

@@
 \begin{abstract}
-  npm (Node Package Manager) is a popular package manager owned by Microsoft that allows developers
+  npm (Node Package Manager) is a popular package manager owned by GitHub that allows developers
   to share node packages and libraries. This article will review and analyze the design flaw of npm
-  and how it was broken by a single package. This article will also review how Microsoft responded to
+  and how it was broken by a single package. This article will also review how GitHub responded to
   the incident and what actions they took to prevent it from happening again.
@@
   <concept>
-  <concept_id>10003456.10003462.10003561.10003563</concept_id>
-  <concept_desc>Social and professional topics~Network access restrictions</concept_desc>
+  <concept_id>10011007.10011074.10011134</concept_id>
+  <concept_desc>Software and its engineering~Collaboration in software development</concept_desc>
+  <concept_significance>500</concept_significance>
+  </concept>
+  <concept>
+  <concept_id>10003456.10003462.10003463</concept_id>
+  <concept_desc>Social and professional topics~Intellectual property</concept_desc>
+  <concept_significance>100</concept_significance>
+  </concept>
+  <concept>
+  <concept_id>10003456.10003457.10003490.10003491.10003495</concept_id>
+  <concept_desc>Social and professional topics~Systems analysis and design</concept_desc>
   <concept_significance>300</concept_significance>
@@
   <concept>
-  <concept_id>10003456.10003462.10003561.10003566</concept_id>
-  <concept_desc>Social and professional topics~Universal access</concept_desc>
+  <concept_id>10003456.10003457.10003490.10003491.10003492</concept_id>
+  <concept_desc>Social and professional topics~Project management techniques</concept_desc>
+  <concept_significance>300</concept_significance>
+  </concept>
+  <concept>
+  <concept_id>10003456.10003457.10003490.10003491.10003496</concept_id>
+  <concept_desc>Social and professional topics~Systems development</concept_desc>
   <concept_significance>100</concept_significance>
@@
   <concept>
-  <concept_id>10003456.10003462.10003574.10003000</concept_id>
-  <concept_desc>Social and professional topics~Social engineering attacks</concept_desc>
-  <concept_significance>500</concept_significance>
+  <concept_id>10003456.10003457.10003490.10003503</concept_id>
+  <concept_desc>Social and professional topics~Software management</concept_desc>
+  <concept_significance>300</concept_significance>
   </concept>
   <concept>
-  <concept_id>10003456.10003462.10003574.10003578</concept_id>
-  <concept_desc>Social and professional topics~Malware / spyware crime</concept_desc>
-  <concept_significance>100</concept_significance>
+  <concept_id>10003456.10003457.10003490.10003507.10003508</concept_id>
+  <concept_desc>Social and professional topics~Centralization / decentralization</concept_desc>
+  <concept_significance>300</concept_significance>
   </concept>
   <concept>
-  <concept_id>10002978.10002991</concept_id>
-  <concept_desc>Security and privacy~Security services</concept_desc>
-  <concept_significance>500</concept_significance>
-  </concept>
-  <concept>
-  <concept_id>10002978.10003006</concept_id>
-  <concept_desc>Security and privacy~Systems security</concept_desc>
+  <concept_id>10003456.10003457.10003490.10003507.10003509</concept_id>
+  <concept_desc>Social and professional topics~Technology audits</concept_desc>
   <concept_significance>500</concept_significance>
@@
 
-\ccsdesc[500]{Security and privacy~Security services}
-\ccsdesc[500]{Security and privacy~Systems security}
-\ccsdesc[300]{Social and professional topics~Network access restrictions}
-\ccsdesc[500]{Social and professional topics~Social engineering attacks}
-\ccsdesc[100]{Social and professional topics~Universal access}
-\ccsdesc[100]{Social and professional topics~Malware / spyware crime}
+\ccsdesc[500]{Software and its engineering~Collaboration in software development}
+\ccsdesc[100]{Social and professional topics~Intellectual property}
+\ccsdesc[300]{Social and professional topics~Systems analysis and design}
+\ccsdesc[300]{Social and professional topics~Project management techniques}
+\ccsdesc[100]{Social and professional topics~Systems development}
+\ccsdesc[300]{Social and professional topics~Software management}
+\ccsdesc[300]{Social and professional topics~Centralization / decentralization}
+\ccsdesc[500]{Social and professional topics~Technology audits}
 
@@
 \subsection{Everything's Creation}
-In 2023, a developer by the name PatrickJS decided to work on a package called `everything'.
-He teamed up with Evan Boehs, another developer to work on creating an npm package that
-would declare every single package in the npm registry as a dependency. This invovled
-working around some obscure npm limitations, such as the maximum number of dependencies
-being around 800 \cite{youtube-everything}, and the maxiumum package size being 10 MB \cite{youtube-everything}.
+In December 2023, a developer by the name PatrickJS decided to work on a package
+called `everything'. He teamed up with Evan Boehs, another developer to work on
+creating an npm package that would declare every single package in the npm
+registry as a dependency. This invovled working around some obscure npm
+limitations, such as the maximum number of dependencies being around 800
+\cite{youtube-everything}, and the maxiumum package size being 10 MB
+\cite{youtube-everything}.
 
@@
 
-\subsection{Response}
+\subsection{Developer's Response}
 PatrickJS and Evan Boehs weren't aware of the consequences of their actions
@@
 
-\section{Microsoft's Response}
+uncenter, a developer who assisted in the creation of the `everything' package,
+wrote:
+
+`We immediately reached out to GitHub; Patrick used his network and contacts to
+speak to people at GitHub, and we sent multiple emails to the support and
+security teams on NPM. Unfortunately, these events transpired over the holidays
+and the NPM/GitHub teams were not responding (likely out of the office). We
+continued to get harsh and rude comments from random people with a little too
+much time on their hands... one person even wrote a 1400 word rant about the
+unpublishing issue, despite us repeatedly telling them we could do nothing
+further' \cite{uncenter-blog-everything}.
+
+\section{GitHub's Response}
+Due to this happening over the holidays, it was only until the end of day on Jan
+2, 2024 that GitHub reached out to the developers and notified them that they
+were aware of the problem \cite{uncenter-blog-everything}. The next day (Jan 3rd),
+GitHub flagged the repository and began removing the packages on npm.
+
+\subsection{Review}
+On Jan 4th, GitHub sent a follow-up email to the developers classifying the
+project as against their terms of service, and that they would be removing the
+repository \cite{uncenter-blog-everything}. GitHub removed the repository and
+packages from npm.
+
+\section{Design Flaw Analysis}
+The `everything' incident exposed a fundamental flaw: npm's design allows
+developers to create packages that depend on every other package in the registry,
+or a large number of packages.
+
+\subsection{Proposed Solutions}
+There have been a few proposed solutions to the design flaw of npm.
+It appears that GitHub does not have any immediate plans to change their
+policies judging by their response to the `everything' package incident.
+
+\subsubsection{uncenter} proposes `NPM should either a) prevent folks from
+publishing packages with star versions in the package.json entirely, or b) don't
+consider a dependent of a package if it uses a star version when tallying how
+many packages depend on a package for unpublishing.' \cite{uncenter-blog-everything}.
+
+\subsubsection{PatrickJS} proposes `A) allow folks to unpublish when the
+packages that depend on them use a "star" version, B) not permit star versions
+in published packages going forward' \cite{bleepingcomputer-everything}
+
+At its core, this is a fundamental design flaw of npm. The npm registry is
+designed to be a public registry, and as such, it is difficult to prevent
+developers from creating packages that depend on every other package in the
+registry. This is a problem that is difficult to solve without fundamentally
+changing the design of the npm registry.
+
+\subsection{Other Potential Solutions}
+\subsubsection{Rate Limiting}
+One potential solution to this problem is to rate limit the number of packages
+that a single package can depend on. This would prevent developers from creating
+packages that depend on every other package in the registry.
+
+\subsubsection{Dependency Analysis}
+Another potential solution is to analyze the dependencies of a package before
+allowing it to be published. If a package depends on every other package in the
+registry, it could be flagged for review by the npm team.
+
+\subsubsection{Unpublishing Policies}
+The unpublishing policies that npm put in place after the left-pad incident
+were designed to prevent a similar incident from happening again. However, they
+ended up creating a new design flaw that was exploited by the `everything'
+package. npm could consider revising these policies to prevent a similar
+incident from happening in the future.
+
+\subsubsection{Review Process}
+npm could also consider implementing a review process for new packages that are
+published to the registry and contain a large number of dependencies. This would
+allow the npm team to catch packages like `everything' before they are published
+to the registry.
+
+\section{Conclusion}
+The `everything' package incident was a catastrophic failure that was not
+intended by the developers of the package. It was the result of a design flaw in
+the npm registry. The incident highlights the need for better security and
+reliability in the npm registry, and the need for better policies to prevent
+similar incidents from happening in the future.
+
+\section{Acknowledgements}
+I would like to thank Theo Browne for introducing this recent incident to me
+by the form of a YouTube video \cite{youtube-everything}. I would also like to
+thank the developers of the `everything' package for sharing their story and
+providing valuable insights into the incident.
 
@@
 \appendix
-\section{Reading Resources}
-Azer Koçulu himself wrote a blog post about the incident, which can be found at \cite{medium-azer}.
+\section{Appendix: Reading Resources}
+\begin{itemize}
+  \item Azer Koçulu himself wrote a blog post about the incident, which can be found at \cite{appendix-medium-azer}.
+  \item The everything team created a website advertising the package, which can be found at \cite{appendix-everything-website}.
+\end{itemize}
 

### 2024-02-26 Paper/2/Paper.tex
More work

@@
 \settopmatter{printacmref=false} % Removes citation information below abstract
-\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
+\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with 
+% conference information in first column
 
@@
 \begin{abstract}
-  npm (Node Package Manager) is a popular package manager owned by GitHub that allows developers
-  to share node packages and libraries. This article will review and analyze the design flaw of npm
-  and how it was broken by a single package. This article will also review how GitHub responded to
-  the incident and what actions they took to prevent it from happening again.
+  npm (Node Package Manager) is a popular package manager owned by GitHub that
+  allows developers to share node packages and libraries. This article will
+  review and analyze the design flaw of npm and how it was broken by a single
+  package, and will also review how GitHub responded to the incident and what
+  actions they took in response.
 \end{abstract}
 
-\keywords{npm, design flaws, everything, left-pad}
+\keywords{npm, github, design flaws, everything, left-pad}
 
 \begin{CCSXML}
-  <ccs2012>
-  <concept>
-  <concept_id>10011007.10011074.10011134</concept_id>
-  <concept_desc>Software and its engineering~Collaboration in software development</concept_desc>
-  <concept_significance>500</concept_significance>
-  </concept>
-  <concept>
-  <concept_id>10003456.10003462.10003463</concept_id>
-  <concept_desc>Social and professional topics~Intellectual property</concept_desc>
-  <concept_significance>100</concept_significance>
-  </concept>
-  <concept>
+  <ccs2012> <concept> <concept_id>10011007.10011074.10011134</concept_id>
+  <concept_desc>Software and its engineering~Collaboration in software
+  development</concept_desc> <concept_significance>500</concept_significance>
+  </concept> <concept> <concept_id>10003456.10003462.10003463</concept_id>
+  <concept_desc>Social and professional topics~Intellectual
+  property</concept_desc> <concept_significance>100</concept_significance>
+  </concept> <concept>
   <concept_id>10003456.10003457.10003490.10003491.10003495</concept_id>
-  <concept_desc>Social and professional topics~Systems analysis and design</concept_desc>
-  <concept_significance>300</concept_significance>
-  </concept>
-  <concept>
+  <concept_desc>Social and professional topics~Systems analysis and
+  design</concept_desc> <concept_significance>300</concept_significance>
+  </concept> <concept>
   <concept_id>10003456.10003457.10003490.10003491.10003492</concept_id>
-  <concept_desc>Social and professional topics~Project management techniques</concept_desc>
-  <concept_significance>300</concept_significance>
-  </concept>
-  <concept>
+  <concept_desc>Social and professional topics~Project management
+  techniques</concept_desc> <concept_significance>300</concept_significance>
+  </concept> <concept>
   <concept_id>10003456.10003457.10003490.10003491.10003496</concept_id>
-  <concept_desc>Social and professional topics~Systems development</concept_desc>
-  <concept_significance>100</concept_significance>
-  </concept>
-  <concept>
+  <concept_desc>Social and professional topics~Systems
+  development</concept_desc> <concept_significance>100</concept_significance>
+  </concept> <concept>
   <concept_id>10003456.10003457.10003490.10003503</concept_id>
-  <concept_desc>Social and professional topics~Software management</concept_desc>
-  <concept_significance>300</concept_significance>
-  </concept>
-  <concept>
+  <concept_desc>Social and professional topics~Software
+  management</concept_desc> <concept_significance>300</concept_significance>
+  </concept> <concept>
   <concept_id>10003456.10003457.10003490.10003507.10003508</concept_id>
-  <concept_desc>Social and professional topics~Centralization / decentralization</concept_desc>
-  <concept_significance>300</concept_significance>
-  </concept>
-  <concept>
+  <concept_desc>Social and professional topics~Centralization /
+  decentralization</concept_desc>
+  <concept_significance>300</concept_significance> </concept> <concept>
   <concept_id>10003456.10003457.10003490.10003507.10003509</concept_id>
   <concept_desc>Social and professional topics~Technology audits</concept_desc>
-  <concept_significance>500</concept_significance>
-  </concept>
-  </ccs2012>
+  <concept_significance>500</concept_significance> </concept> </ccs2012>
 \end{CCSXML}
@@
 \section{Article Introduction}
-Design flaws in software can sometimes lead to security breaches. More often than
-not, it is these types of breaches that are the most popularized. However, sometimes
-a design flaw can lead to a catastrophic failure that was not even intended
-(or initiated) by a bad actor.
-With over 1.3 million packages as of April 14th, 2021 \cite{npmblog-stats}, npm is
-the world's largest software registry \cite{aboutnpm,w3schools}. As a
-result, it has been heavily relied upon by developers for years.
+Design flaws in software can sometimes lead to security breaches. More often
+than not, it is these types of design flaws that are the most popularized.
+However, sometimes a design flaw can lead to a catastrophic failure that was not
+even intended (or initiated) by a bad actor. With over 1.3 million packages as
+of April 14th, 2021 \cite{npmblog-stats}, npm is the world's largest software
+registry \cite{aboutnpm,w3schools}. As a result, it has been heavily relied upon
+by developers for years.
 
-Needless to say, the npm registry is a critical piece of infrastructure for the
-entire JavaScript community (and by extension 99\% of websites \cite{w3techs}). Developers
-expected that the npm registry would be reliable, secure, and complete. However, the
-left-pad incident in 2016 \cite{npmblog-leftpad} and the everything package incident
-in 2023 \cite{youtube-everything} have shown that the npm registry is not as reliable
-as developers had hoped.
+The npm registry is a critical piece of infrastructure for the entire JavaScript
+community (and by extension, 99\% of websites \cite{w3techs}). Developers expect
+that the npm registry would be reliable, secure, and complete. However, the
+left-pad incident in 2016 \cite{npmblog-leftpad} and the everything package
+incident in 2023 \cite{youtube-everything} have shown that the npm registry is
+not as reliable as developers had hoped.
 
@@
 Azer Koçulu is a software developer who was working on a personal project called
-kik \cite{qz}. Coincidentally, Kik was also the name of a company in
-Ontario, Canada \cite{qz, crunchbase}. The company reached out to Koçulu
-requesting that he change the name of his project. Koçulu refused, and the company
-proceeded to file a complaint with npm \cite{qz}. npm then decided to transfer the name
-kik to the company, which caused Koçulu to remove all of his packages from the
-npm registry, stating
+kik \cite{qz}. Coincidentally, Kik was also the name of a company in Ontario,
+Canada \cite{qz, crunchbase}. The company reached out to Koçulu requesting that
+he change the name of his project. Koçulu refused, and the company proceeded to
+file a complaint with npm \cite{qz}. npm then decided to transfer the name kik
+to the company, which caused Koçulu to remove all of his packages from the npm
+registry, stating
 
-"I want all my modules to be deleted including my account, along with this package.
-I don't wanna be a part of NPM anymore. If you don't do it, let me know how do it quickly.
-I think I have the right of deleting all my stuff from NPM." \cite{medium-mikeroberts}
+"I want all my modules to be deleted including my account, along with this
+package. I don't wanna be a part of NPM anymore. If you don't do it, let me know
+how do it quickly. I think I have the right of deleting all my stuff from NPM."
+\cite{medium-mikeroberts}
 
 \subsection{The left-pad package}
-As a result of Koçulu's deciscion, all of his packages (including left-pad) were removed
-from the npm registry. Despite being only 17 lines of code \cite{github-leftpad-code},
-millions of packages relied on left-pad \cite{github-leftpad-dependency}. As a result,
-many packages that directly or indirectly relied on left-pad broke, including React,
-Babel, and Atom.
+As a result of Koçulu's deciscion, all of his packages (including left-pad) were
+removed from the npm registry. Despite being only 17 lines of code
+\cite{github-leftpad-code}, millions of packages relied on left-pad
+\cite{github-leftpad-dependency}. As a result, many packages that directly or
+indirectly relied on left-pad broke, including React, Babel, and Atom
+\cite{npmblog-leftpad}.
 
-After an attempt to publish left-pad under a new version failed (due to some major
-dependencies relying on the old version specificially, which was no longer available),
-npm resulted to restoring the package from a backup \cite{npmblog-leftpad}. The total
-downtime taken to restore the backup was 2.5 hours \cite{npmblog-leftpad}.
+After an attempt to publish left-pad under a new version failed (due to some
+major dependencies relying on the old version specificially, which was no longer
+available), npm resulted to restoring the package from a backup
+\cite{npmblog-leftpad}. The total downtime taken to restore the backup was 2.5
+hours \cite{npmblog-leftpad}.
 
-With the first ever unprecedented un-unpublishing of a package, npm was able to restore
-the left-pad package and the packages that relied on it.
+With the first ever unprecedented un-unpublishing of a package, npm was able to
+restore the left-pad package and the packages that relied on it
+\cite{npmblog-leftpad}.
 
@@
 Once the left-pad incident was resolved, npm published a blog post detailing the
-incident and the steps they planned to take to prevent it from happening again \cite{npmblog-leftpad}.
+incident and the steps they planned to take to prevent it from happening again
+\cite{npmblog-leftpad}.
 
-`We will make it harder to un-publish a version of a package if doing so would break other packages.
-We are still fleshing out the technical details of how this will work. Like any registry change,
-we will of course take our time to consider and implement it with care.' \cite{npmblog-leftpad}
+`We will make it harder to un-publish a version of a package if doing so would
+break other packages. We are still fleshing out the technical details of how
+this will work. Like any registry change, we will of course take our time to
+consider and implement it with care.' \cite{npmblog-leftpad}
 
-npm ended up enacting two policies relating to unpublishing packages. The first policy applied on
-packages that were less than 72 hours old, allowing unpublishing as long as `no other packages
-in the npm Public Registry depend on your package' \cite{npm-docs-unpublishing}.
+npm ended up enacting two policies relating to unpublishing packages. The first
+policy applied on packages that were less than 72 hours old, allowing
+unpublishing as long as `no other packages in the npm Public Registry depend on
+your package' \cite{npm-docs-unpublishing}.
 
-The second policy applied to packages that were older than 72 hours, allowing unpublishing as long
-as three conditions were met \cite{npm-docs-unpublishing}:
+The second policy applied to packages that were older than 72 hours, allowing
+unpublishing as long as three conditions were met \cite{npm-docs-unpublishing}:
 \begin{enumerate}
@@
 
-With these new policies in place, npm hoped to prevent a similar incident from happening again.
-However, these new policies lead towards a new design flaw.
+With these new policies in place, npm hoped to prevent a similar incident from
+happening again. However, these new policies lead towards a new unforseen design
+flaw.
 
@@
 In December 2023, a developer by the name PatrickJS decided to work on a package
-called `everything'. He teamed up with Evan Boehs, another developer to work on
-creating an npm package that would declare every single package in the npm
-registry as a dependency. This invovled working around some obscure npm
-limitations, such as the maximum number of dependencies being around 800
-\cite{youtube-everything}, and the maxiumum package size being 10 MB
-\cite{youtube-everything}.
+called `everything'. He teamed up with Evan Boehs and a few other developers to
+work on creating an npm package that would declare every package in the npm
+registry as a dependency \cite{uncenter-blog-everything}. This invovled working
+around obscure npm limitations, such as the maximum number of dependencies being
+around 800 \cite{uncenter-blog-everything, youtube-everything}, and the maxiumum
+package size being 10 MB \cite{uncenter-blog-everything, youtube-everything}.
 
-In order to work around these limitations, PatrickJS and Evan Boehs decided to chunk their
-dependencies into smaller packages \lstinline|@everything-registry/chunk-0| through to \\
-\lstinline|@everything-registry/chunk-4|. At the time there was approximately 2.5 million
-packages in the npm registry \cite{youtube-everything}, so sub-chunking was also required.
+In order to work around these limitations, PatrickJS and Evan Boehs decided to
+chunk their dependencies into smaller packages
+\lstinline|@everything-registry/chunk-0| through to \\
+\lstinline|@everything-registry/chunk-4|. At the time there was approximately
+2.5 million packages in the npm registry \cite{youtube-everything}, so
+sub-chunking was also required \cite{youtube-everything}.
 
-Unsurprisingly, npm also has a rate limit on how quickly packages can be published. Thus,
-PatrickJS and Evan Boehs used a GitHub Action workflow to publish the packages \cite{youtube-everything}.
+Unsurprisingly, npm also has a rate limit on how quickly packages can be
+published \cite{npm-ratelimiting}. Thus, PatrickJS and Evan Boehs used a GitHub
+Action workflow to publish the packages
+\cite{youtube-everything,uncenter-blog-everything}.
 
@@
 
-This was also caused by the fact that the `everything' package depended on a `*' version
-of all of its packages, which meant that it matched any version of each of its packages.
+This was also caused by the fact that the `everything' package depended on a `*'
+version of all of its packages, which meant that it matched any version of each
+of its packages. Even if developers published a new version of their packages,
+the `everything' package would actually just depend on both the old and new
+versions of the package \cite{uncenter-blog-everything}.
 
 \subsection{Historic Related Incidents}
-npm was not a stranger to packages and projects before `everything'.
+npm was no a stranger to packages and projects similar to `everything'.
 
 \subsubsection{no-one-left-behind}
-was an npm package that was created in 2018 that similarly depended
-on 1,000 npm packages \cite{npm-no-one-left-behind-dependencies}. npm managed to remove
-the package before it caused significant damage \cite{npm-no-one-left-behind-security}.
-It was then re-uploaded under a different name, this time with 33,000 dependencies \cite{socket-everything}.
+was an npm package that was created in 2018 that depended on 1,000 npm packages
+\cite{npm-no-one-left-behind-dependencies}. npm managed to remove the package
+before it caused significant damage \cite{npm-no-one-left-behind-security}. It
+was then re-uploaded under a different name, this time with 33,000 dependencies
+\cite{socket-everything}.
 
 \subsubsection{hoarders}
-was a package created by Josh Holbrook that was created near the conception of npm (2012) that
-also depended on 11,000 packages at its inception \cite{github-hoarders-dependencies}.
-Isaac Schluter (the founder of npm) talked with the creator of the package and convinced
-him to unpublish it \cite{github-hoarders}.  A few years later in Aug 19, 2021, Josh Holbrook
-found a way to work around having a heavy load on npm.
+was a package created by Josh Holbrook that was created near the conception of
+npm (2012) that also depended on 11,000 packages at its inception
+\cite{github-hoarders-dependencies}. Isaac Schluter (the founder of npm) talked
+with the creator of the package and convinced him to unpublish it
+\cite{github-hoarders}.  A few years later in Aug 19, 2021, Josh Holbrook found
+a way to work around having a heavy load on npm.
 
@@
 2, 2024 that GitHub reached out to the developers and notified them that they
-were aware of the problem \cite{uncenter-blog-everything}. The next day (Jan 3rd),
-GitHub flagged the repository and began removing the packages on npm.
+were aware of the problem \cite{uncenter-blog-everything}. The next day (Jan
+3rd), GitHub flagged the repository and began removing the packages on npm.
 
@@
 The `everything' incident exposed a fundamental flaw: npm's design allows
-developers to create packages that depend on every other package in the registry,
-or a large number of packages.
+developers to create packages that depend on every other package in the
+registry, or a large number of packages.
 
 \subsection{Proposed Solutions}
-There have been a few proposed solutions to the design flaw of npm.
-It appears that GitHub does not have any immediate plans to change their
-policies judging by their response to the `everything' package incident.
+There have been a few proposed solutions to the design flaw of npm. It appears
+that GitHub does not have any immediate plans to change their policies judging
+by their response to the `everything' package incident
+\cite{uncenter-blog-everything}.
 
@@
 consider a dependent of a package if it uses a star version when tallying how
-many packages depend on a package for unpublishing.' \cite{uncenter-blog-everything}.
+many packages depend on a package for unpublishing.'
+\cite{uncenter-blog-everything}.
 
@@
 
+Realistically, an initial package should not depend on more than a few hundred
+other packages (especially not directly). This would be a good indicator that
+the package is not well-designed, and would allow the npm team to review the
+package before allowing it to be published.
+
+The idea of rate-limiting the growth of a package's dependencies would require
+careful consideration and implementation, as it could potentially break existing
+packages that rely on a large number of dependencies.
+
 \subsubsection{Dependency Analysis}
@@
 allowing it to be published. If a package depends on every other package in the
-registry, it could be flagged for review by the npm team.
+registry (or a significant portion of it), it could be flagged for review by the
+npm team.
+
+Static code analysis could additionally be used to detect dependencies that are
+not actually used by the package, and flag the package for review.
 
 \subsubsection{Unpublishing Policies}
-The unpublishing policies that npm put in place after the left-pad incident
-were designed to prevent a similar incident from happening again. However, they
-ended up creating a new design flaw that was exploited by the `everything'
-package. npm could consider revising these policies to prevent a similar
-incident from happening in the future.
+The unpublishing policies that npm put in place after the left-pad incident were
+designed to prevent a similar incident from happening again. However, they ended
+up creating a new design flaw that was exploited by the `everything' package.
+npm could consider revising these policies to prevent a similar incident from
+happening in the future.
+
+While there may not be a perfect policy that works for every package, npm could
+consider implementing a review process for new packages that are published to
+the registry from new developer (accounts), or from developers that have not
+published a package in a long time.
 
@@
 to the registry.
+
+Such a review process would require some form of automation and user reporting
+system. Considering npm is free to use \cite{npm-tos}, it may not be feasible to
+have sufficient staffing for this process.
+
+\subsubsection{Accept the Flaw}
+The route that GitHub seems to take (for now at least) is to accept the flaw and
+mark packages like `everything' as against their terms of service
+\cite{uncenter-blog-everything}. While this may have worked in the case of the
+`everything' package, it is not a long-term solution to the problem. GitHub will
+most likely have to automate some form of detection and removal of packages like
+`everything' in the future.
 
@@
 \section{Acknowledgements}
-I would like to thank Theo Browne for introducing this recent incident to me
-by the form of a YouTube video \cite{youtube-everything}. I would also like to
+I would like to thank Theo Browne for introducing this recent incident to me by
+the form of a YouTube video \cite{youtube-everything}. I would also like to
 thank the developers of the `everything' package for sharing their story and
@@
 \begin{itemize}
-  \item Azer Koçulu himself wrote a blog post about the incident, which can be found at \cite{appendix-medium-azer}.
-  \item The everything team created a website advertising the package, which can be found at \cite{appendix-everything-website}.
+  \item Azer Koçulu himself wrote a blog post about the incident, which can be
+        found at \cite{appendix-medium-azer}.
+  \item The everything team created a website advertising the package, which can
+        be found at \cite{appendix-everything-website}.
 \end{itemize}

### 2024-02-27 Paper/2/Paper.tex
More rewording

@@
   npm (Node Package Manager) is a popular package manager owned by GitHub that
-  allows developers to share node packages and libraries. This article will
+  allows developers to share node packages and libraries \cite{npm}. This article will
   review and analyze the design flaw of npm and how it was broken by a single
@@
 community (and by extension, 99\% of websites \cite{w3techs}). Developers expect
-that the npm registry would be reliable, secure, and complete. However, the
+that the npm registry will be reliable, secure, and complete. However, the
 left-pad incident in 2016 \cite{npmblog-leftpad} and the everything package
 incident in 2023 \cite{youtube-everything} have shown that the npm registry is
-not as reliable as developers had hoped.
+not as mature as developers had hoped.
 
@@
 he change the name of his project. Koçulu refused, and the company proceeded to
-file a complaint with npm \cite{qz}. npm then decided to transfer the name kik
-to the company, which caused Koçulu to remove all of his packages from the npm
+file a complaint with npm \cite{qz}. npm (following its Dispute Resolutinon
+Policy \cite{npm-dispute-policy}) then decided to transfer the name kik to the
+company, which caused Koçulu to remove all of his packages from the npm
 registry, stating
@@
 Unsurprisingly, npm also has a rate limit on how quickly packages can be
-published \cite{npm-ratelimiting}. Thus, PatrickJS and Evan Boehs used a GitHub
-Action workflow to publish the packages
+published \cite{npm-ratelimiting,github-npm-ratelimiting}. Thus, PatrickJS and
+Evan Boehs used a GitHub Action workflow to publish the packages
 \cite{youtube-everything,uncenter-blog-everything}.

### 2024-02-27 Paper/2/Paper.tex
Almost done?!

@@
   npm (Node Package Manager) is a popular package manager owned by GitHub that
-  allows developers to share node packages and libraries \cite{npm}. This article will
-  review and analyze the design flaw of npm and how it was broken by a single
-  package, and will also review how GitHub responded to the incident and what
-  actions they took in response.
+  allows developers to share javascript packages and libraries \cite{npm}. This
+  article will review and analyze the design flaw of npm and how it was broken
+  by a single package, and will also review how GitHub responded to the
+  incident.
 \end{abstract}
@@
 left-pad incident in 2016 \cite{npmblog-leftpad} and the everything package
-incident in 2023 \cite{youtube-everything} have shown that the npm registry is
+incident in 2023 \cite{youtube-everything} has shown that the npm registry is
 not as mature as developers had hoped.
@@
 Azer Koçulu is a software developer who was working on a personal project called
-kik \cite{qz}. Coincidentally, Kik was also the name of a company in Ontario,
-Canada \cite{qz, crunchbase}. The company reached out to Koçulu requesting that
-he change the name of his project. Koçulu refused, and the company proceeded to
-file a complaint with npm \cite{qz}. npm (following its Dispute Resolutinon
-Policy \cite{npm-dispute-policy}) then decided to transfer the name kik to the
-company, which caused Koçulu to remove all of his packages from the npm
-registry, stating
+kik \cite{qz}. Coincidentally, Kik is also the name of a company in Ontario,
+Canada \cite{qz, crunchbase}. On March 11 2016, the company reached out to
+Koçulu requesting that he change the name of his project. Koçulu refused, and
+the company proceeded to file a complaint with npm \cite{qz}. npm (following its
+Dispute Resolutinon Policy \cite{npm-dispute-policy}) decided to transfer the
+name kik to the company. In response, Koçulu decided to remove all of his
+packages from the npm registry, stating
 
@@
 After an attempt to publish left-pad under a new version failed (due to some
-major dependencies relying on the old version specificially, which was no longer
+dependencies relying on the older version specificially, which was no longer
 available), npm resulted to restoring the package from a backup
@@
 npm ended up enacting two policies relating to unpublishing packages. The first
-policy applied on packages that were less than 72 hours old, allowing
+policy applied on packages less than 72 hours old, allowing
 unpublishing as long as `no other packages in the npm Public Registry depend on
@@
 
-The second policy applied to packages that were older than 72 hours, allowing
+The second policy applied to packages older than 72 hours, allowing
 unpublishing as long as three conditions were met \cite{npm-docs-unpublishing}:
@@
 
-This was also caused by the fact that the `everything' package depended on a `*'
-version of all of its packages, which meant that it matched any version of each
-of its packages. Even if developers published a new version of their packages,
-the `everything' package would actually just depend on both the old and new
-versions of the package \cite{uncenter-blog-everything}.
+A contributing factor to the incident was that the `everything' package was that
+the `everything' package depended on a `*' version of all of its packages, which
+meant that it matched any version of each of its packages. Even if developers
+published a new version of their packages, the `everything' package would
+actually just depend on both the old and new versions of the package
+\cite{uncenter-blog-everything}.
 
@@
 npm was no a stranger to packages and projects similar to `everything'.
+
+\subsubsection{hoarders}
+was a package created by Josh Holbrook that was created near the conception of
+npm (2012) that also depended on 11,000 packages at its inception
+\cite{github-hoarders-dependencies}. Isaac Schlueter (the founder of npm) talked
+with the creator of the package and convinced him to unpublish it to avoid
+performance issues with npm \cite{github-hoarders}.  Nearly a decade later on
+Aug 19, 2021, Josh Holbrook found a way to work around having a heavy impact on
+npm.
+
+`now, rather than installing the utilities as direct dependencies, hoarders
+installs them lazily, on-the-fly. this change is practically seamless - simply
+reach for the utility like you would normally and hoarders will do the rest! the
+only requirements are npm and an internet connection.' \cite{github-hoarders}
 
@@
 \cite{socket-everything}.
-
-\subsubsection{hoarders}
-was a package created by Josh Holbrook that was created near the conception of
-npm (2012) that also depended on 11,000 packages at its inception
-\cite{github-hoarders-dependencies}. Isaac Schluter (the founder of npm) talked
-with the creator of the package and convinced him to unpublish it
-\cite{github-hoarders}.  A few years later in Aug 19, 2021, Josh Holbrook found
-a way to work around having a heavy load on npm.
-
-`now, rather than installing the utilities as direct dependencies, hoarders
-installs them lazily, on-the-fly. this change is practically seamless - simply
-reach for the utility like you would normally and hoarders will do the rest! the
-only requirements are npm and an internet connection.' \cite{github-hoarders}
 
@@
 \section{GitHub's Response}
-Due to this happening over the holidays, it was only until the end of day on Jan
-2, 2024 that GitHub reached out to the developers and notified them that they
-were aware of the problem \cite{uncenter-blog-everything}. The next day (Jan
-3rd), GitHub flagged the repository and began removing the packages on npm.
+Due to this happening over the holidays, it was only until the evening of Jan 2,
+2024 that GitHub reached out to the developers and notified them that they were
+aware of the problem \cite{uncenter-blog-everything}. The next day (Jan 3rd),
+GitHub flagged the repository and began removing the packages on npm.
 
-\subsection{Review}
+\subsection{Follow Up}
 On Jan 4th, GitHub sent a follow-up email to the developers classifying the
@@
 repository \cite{uncenter-blog-everything}. GitHub removed the repository and
-packages from npm.
+packages from npm the same day \cite{scmagazine-everything-blog}.
 
 \section{Design Flaw Analysis}
-The `everything' incident exposed a fundamental flaw: npm's design allows
-developers to create packages that depend on every other package in the
-registry, or a large number of packages.
+The `everything' incident exposed a fundamental flaw: npm's handling of
+unpublishing and dependencies was not as robust as it should have been. npm
+had gone from one package being removed breaking many packages, to one package
+being added preventing other packages from being removed.
 
@@
 
+\subsection{Other Potential Solutions}
 At its core, this is a fundamental design flaw of npm. The npm registry is
-designed to be a public registry, and as such, it is difficult to prevent
-developers from creating packages that depend on every other package in the
-registry. This is a problem that is difficult to solve without fundamentally
-changing the design of the npm registry.
+designed to be a public registry, and as such, it is difficult to reliably allow
+developers to unpublish resources without impacting others. This is a problem
+that is difficult to solve without fundamentally changing the design of the npm
+registry.
 
-\subsection{Other Potential Solutions}
 \subsubsection{Rate Limiting}
@@
 
-\subsubsection{Dependency Analysis}
-Another potential solution is to analyze the dependencies of a package before
-allowing it to be published. If a package depends on every other package in the
-registry (or a significant portion of it), it could be flagged for review by the
-npm team.
+% \subsubsection{Dependency Analysis}
+% Another potential solution is to analyze the dependencies of a package before
+% allowing it to be published. If a package depends on every other package in the
+% registry (or a significant portion of it), it could be flagged for review by the
+% npm team.
 
-Static code analysis could additionally be used to detect dependencies that are
-not actually used by the package, and flag the package for review.
+% Static code analysis could additionally be used to detect dependencies that are
+% not actually used by the package, and flag the package for review.
 
@@
 \section{Appendix: Reading Resources}
-\begin{itemize}
-  \item Azer Koçulu himself wrote a blog post about the incident, which can be
-        found at \cite{appendix-medium-azer}.
-  \item The everything team created a website advertising the package, which can
-        be found at \cite{appendix-everything-website}.
-\end{itemize}
+Azer Koçulu himself wrote a blog post about the incident, which can be found at
+\cite{appendix-medium-azer}. \\
+The everything team created a website advertising the package, which can be
+found at \cite{appendix-everything-website}.
 
